# Model 

## Selecting modelling technique 

The modelling technique that we will be using are the following:


| n°  | Model                      | Function in R |
|:---:|:---------------------------|:--------------|
|  1  | Logistic regression models |    GLM        |
|  2  | Decision trees             |   CART        |
|  3  | Discriminate analysis      | 1) lda <br /> 2) qda <br /> 3) mda <br /> 4) fda |
|  4  | Random forest              |  randomForest |
|  5  | XGBoost                    |    xgboost    |

 
## Generate test design

We start by creating a training and test set based on the data, this will be done by dividing it in a randomly selection into the two subsets, with 75% of the data in the training and the remaining 25% in the test.

```{r test and training sets}

#library(caret)

#so that we always have the same division
set.seed(2311)

#creation of the index to divide the data in the two subsets
val_index<-createDataPartition(data_sel$RESPONSE, p=0.75, list=FALSE)

#training dataset
TrainData<-data_sel[val_index,]
#test dataset
TestData <- data_sel[-val_index,]

```


```{r confusion matrix draw function}

draw_confusion_matrix <- function(cm) {

  layout(matrix(c(1,1,2)))
  par(mar=c(2,2,2,2))
  plot(c(100, 345), c(300, 450), type = "n", xlab="", ylab="", xaxt='n', yaxt='n')
  title('CONFUSION MATRIX', cex.main=2)

  # create the matrix 
  rect(150, 430, 240, 370, col='#3F97D0')
  text(195, 435, 'Class1', cex=1.2)
  rect(250, 430, 340, 370, col='#F7AD50')
  text(295, 435, 'Class2', cex=1.2)
  text(125, 370, 'Predicted', cex=1.3, srt=90, font=2)
  text(245, 450, 'Actual', cex=1.3, font=2)
  rect(150, 305, 240, 365, col='#F7AD50')
  rect(250, 305, 340, 365, col='#3F97D0')
  text(140, 400, 'Class1', cex=1.2, srt=90)
  text(140, 335, 'Class2', cex=1.2, srt=90)

  # add in the cm results 
  res <- as.numeric(cm$table)
  text(195, 400, res[1], cex=1.6, font=2, col='white')
  text(195, 335, res[2], cex=1.6, font=2, col='white')
  text(295, 400, res[3], cex=1.6, font=2, col='white')
  text(295, 335, res[4], cex=1.6, font=2, col='white')

  # add in the specifics 
  plot(c(100, 0), c(100, 0), type = "n", xlab="", ylab="", 
       main = "DETAILS", xaxt='n', yaxt='n')
  text(10, 85, names(cm$byClass[1]), cex=1.2, font=2)
  text(10, 70, round(as.numeric(cm$byClass[1]), 3), cex=1.2)
  text(30, 85, names(cm$byClass[2]), cex=1.2, font=2)
  text(30, 70, round(as.numeric(cm$byClass[2]), 3), cex=1.2)
  text(50, 85, names(cm$byClass[5]), cex=1.2, font=2)
  text(50, 70, round(as.numeric(cm$byClass[5]), 3), cex=1.2)
  text(70, 85, names(cm$byClass[6]), cex=1.2, font=2)
  text(70, 70, round(as.numeric(cm$byClass[6]), 3), cex=1.2)
  text(90, 85, names(cm$byClass[7]), cex=1.2, font=2)
  text(90, 70, round(as.numeric(cm$byClass[7]), 3), cex=1.2)

  # add in the accuracy information 
  text(30, 35, names(cm$overall[1]), cex=1.5, font=2)
  text(30, 20, round(as.numeric(cm$overall[1]), 3), cex=1.4)
  text(70, 35, names(cm$overall[2]), cex=1.5, font=2)
  text(70, 20, round(as.numeric(cm$overall[2]), 3), cex=1.4)
}  

```

Firstly, we need to standardize the data, as the variables have different scales. We will normlize the continuous variables. 

```{r scaling}

#selecting only the continuous variables to scale them

data_scale <- data_sel %>% 
                select(DURATION, AMOUNT, INSTALL_RATE, AGE, NUM_CREDITS) %>% 
                scale() %>%  #normalization
                as.data.frame()

#recreating the other variables to add them back to the dataset of the scaled ones 

data_scale %<>% mutate(
  OBS = data_sel$OBS,
  CHK_ACCT = data_sel$CHK_ACCT,
  HISTORY = data_sel$HISTORY,
  PURPOSE = data_sel$PURPOSE,
  SAV_ACCT = data_sel$SAV_ACCT,
  EMPLOYMENT = data_sel$EMPLOYMENT,
  SEX_MALE = data_sel$SEX_MALE,
  MALE_SINGLE = data_sel$MALE_SINGLE,
  MALE_MAR_WID = data_sel$MALE_MAR_WID,
  CO_APPLICANT = data_sel$CO_APPLICANT,
  GUARANTOR = data_sel$GUARANTOR,
  PRESENT_RESIDENT = data_sel$PRESENT_RESIDENT,
  PROPERTY = data_sel$PROPERTY,
  OTHER_INSTALL = data_sel$OTHER_INSTALL,
  RESIDENCE = data_sel$RESIDENCE,
  JOB = data_sel$JOB, 
  RESPONSE = data_sel$RESPONSE
)

#reordering variable in the dataset
data_scale %<>% 
  select(OBS,CHK_ACCT,DURATION,HISTORY,PURPOSE,AMOUNT,SAV_ACCT,EMPLOYMENT,
         INSTALL_RATE,SEX_MALE,MALE_SINGLE,MALE_MAR_WID,CO_APPLICANT,GUARANTOR,
         PRESENT_RESIDENT,PROPERTY,AGE,OTHER_INSTALL,RESIDENCE,NUM_CREDITS,JOB,RESPONSE)

```


```{r test and training sets}

#so that we always have the same division
set.seed(2311)

#creation of the index to divide the data in the two subsets
val_index<-createDataPartition(data_scale$RESPONSE, 
                               p=0.75, list=FALSE)

#training dataset
TrainData<-as.data.frame(data_scale[val_index,])

#test dataset
TestData <- data_scale[-val_index,]

```


Let's start with the first model. 

## Build models 

### 1) Logistic Regressions

#### GLM

##### Definition

We will start by giving a definition of this model. 

> Logistic regression is a statistical model that in its basic form uses a logistic function to model a binary dependent variable, although many more complex extensions exist. In regression analysis, logistic regression (or logit regression) is estimating the parameters of a logistic model (a form of binary regression). 
(https://en.wikipedia.org/wiki/Logistic_regression)

##### Fitting the model 

Now we will fit the logistic regression on the training dataset.

```{r glm-model, echo=FALSE, warning=FALSE, message=FALSE}

#Same division
set.seed(1234)

#model
glm.fit <- glm(RESPONSE ~., data = TrainData, family = binomial)
#check outputs
summary(glm.fit)

#check which variable brings more information--> high coefficient = bring high information
temp <- summary(glm.fit)$coeff[-1,4] < 0.05

#condition: yes or not
temp %<>% as.data.frame()  

kable(temp, caption = "Significance of variable")

#remove variable temp
rm(temp) 

```

Here, we can see that the variables that take the highest importance and that are statistically significant for the model are: DURATION, AMOUNT, INSTALL_RATE, CHK_ACCT, HISTORY, the second level of PURPOSE (hence USED_CAR?), SAV_ACCT, MALE_SINGLE, GUARANTOR, OTHER_INSTALL. 

```{r glm coef}

coef(glm.fit) 

```

If we look at the coeffiecient of the different variables we can conclude that DURATION, AMOUNT, INSTALL_RATE and OTHER_INSTALL have a negative effect on the output, meaning that if they increase (in case of duration and amount) or if they are positive (in the case of install_rate and other_install), the probability of having a positive response will decrease, while CHK_ACCT, HISTORY, PURPOSE2,SAV_ACCT, MALE_SINGLE and GUARANTOR have a positive effect on the prediction of the response, meaning that the more they increase (for chk_acct, sav_acct) or if they are positive (for the other variables), the probability of having RESPONSE = 1 will increase. 

##### Predictions and confusion matrix 

```{r predictions}

#probability given the model
glm.probs <- predict(glm.fit, newdata = TestData, type = "response")

#use a cut of 0.5 to give the prediction
glm.pred <- ifelse(glm.probs > 0.5, 1, 0)

```

This are the predictions for the RESPONSE variable, given the glm model. We use them and a thershold of 0.5 to determine the prediction, whether the person we examine will get a credit (RESPONE = 1), or not (RESPONSE = 0).

Then, with the prediction we can build the confusion matrix. 


```{r confusion matrix}

confusionMatrix(as.factor(glm.pred), as.factor(TestData$RESPONSE))
cm <- confusionMatrix(as.factor(glm.pred), as.factor(TestData$RESPONSE))

draw_confusion_matrix(cm)

```

We are more interested in the false prediction of negative outcomes, as it would mean a loss for the company, rather than a false prediction of a positive outcome, hence we will look at the specificity rather than the sensitivity. Here we can see the the prediction of negative values is quite high (above 80% of the time when an element is predicted as negative it if truly negative) and also if it is negative it will be predicted as such. 

However, this can be said to be like this because of the unbalance of the data set. 

```{r balancing dataset}

data_sel %>% select(RESPONSE) %>% group_by(RESPONSE) %>% count()

```

We can see that actually the data is unbalanced but on the other side, indeed we have more instances taking a positive value than the opposite. Hence, we believe that it is not necessary to control for the balanced dataset and redo the analysis. 

### Decision Trees

#### CART

##### Definition

> A Classification And Regression Tree (CART), is a predictive model, which explains how an outcome variable's values can be predicted based on other values. A CART output is a decision tree where each fork is a split in a predictor variable and each end node contains a prediction for the outcome variable.

(source: https://wiki.q-researchsoftware.com/wiki/Machine_Learning_-_Classification_And_Regression_Trees_(CART))

##### Fitting the model 

```{r cart}

#library(rpart)
#library(rpart.plot)
ct.fit <- rpart(RESPONSE ~., method = "class",  
                data = TrainData, #the training data
                control = rpart.control(minsplit = 4, 
                cp = 1e-05) , model = TRUE)

summary(ct.fit)

```


```{r pruning cart, echo=FALSE}

#cp graph
par(pty = "s")
plotcp(ct.fit)

#cp that minimize the tree
bestcp <- ct.fit$cptable[which.min(ct.fit$cptable[,"xerror"]),"CP"]

ct.prune <- prune(ct.fit, cp= bestcp) #before there was cp=0.01

summary(ct.prune)

#first option of graph:
#plot(ct.prune, uniform = TRUE)
#text(ct.prune, cex = 0.4, use.n = TRUE, all = TRUE)

#second option of graph:
rpart.plot(ct.prune, extra=104, box.palette="GnBu",
               branch.lty=3, shadow.col="gray", nn=TRUE)


#partition tree--> lets check later....

library(parsnip)
set.seed(123) ## For consistent jitter

partition_data <- TrainData
partition_data$RESPONSE <- as.factor(partition_data$RESPONSE)

## Build our tree using parsnip (but with rpart as the model engine)

t_tree <-
  decision_tree() %>%
  set_engine("rpart") %>%
  set_mode("classification") %>%
  fit(RESPONSE ~ CHK_ACCT + HISTORY , data = partition_data)

#install.packages("remotes")
#remotes::install_github("grantmcdermott/parttree")
#library(parttree)

## Plot the data and model partitions
partition_data %>%
  ggplot(aes(x=CHK_ACCT, y=HISTORY)) + #axis to check
  geom_jitter(aes(col=RESPONSE), alpha=0.7) +
  geom_parttree(data = t_tree, aes(fill=RESPONSE), alpha = 0.1) +
  theme_minimal()+
  theme_bw()


```

##### Predictions and confusion matrix 

```{r prediction cart}

ct.pred <- predict(ct.prune, newdata = TestData, type = "class")

```


```{r confusion matric cart}

confusionMatrix(as.factor(ct.pred), as.factor(TestData$RESPONSE))
cm <- confusionMatrix(as.factor(ct.pred), as.factor(TestData$RESPONSE))
draw_confusion_matrix(cm)

```

### Discriminate analysis 

#### LDA 

##### Definition

We start by giving the definition of the model. 

> The Latent Dirichlet allocation (LDA) is a generative statistical model that allows sets of observations to be explained by unobserved groups that explain why some parts of the data are similar.


##### Fitting the model

```{r lda model}

#library(MASS)

#model creation
lda.fit <- lda(RESPONSE ~., data = TrainData, subset = TrainData$OBS)

lda.fit

#A Stacked Histogram of the LDA Values 
#The two groups are the groups for response classes.
#plot(lda.fit)

```

##### Predictions and confusion matrix 


```{r lda predictions}

lda.pred <- predict(lda.fit, newdata = TestData)
lda.class <- lda.pred$class


#plot the error of the predictions

par(mfrow=c(1,1))
plot(lda.pred$x[,1], lda.pred$class, col=TestData$RESPONSE+10)
#key takeaway
#The Predicted Group-1 and Group-2 has been colored (red and green). The mix of red and green color in each group shows the incorrect classification prediction.

```

```{r confusion matrix lda}

confusionMatrix(as.factor(lda.class), as.factor(TestData$RESPONSE))
cm <- confusionMatrix(as.factor(lda.class), as.factor(TestData$RESPONSE))

draw_confusion_matrix(cm)
```
 
#### QDA 

##### Definition

> Quadratic Discriminant Analysis is little bit more flexible than LDA, in the sense that it does not assumes the equality of variance/covariance. In other words, for QDA the covariance matrix can be different for each class.

(source: http://www.sthda.com/english/articles/36-classification-methods-essentials/146-discriminant-analysis-essentials-in-r/)

##### Fitting the model 

```{r fit qda}

qda.fit <- qda(RESPONSE ~., data = TrainData, subset = TrainData$OBS)

qda.fit

```

##### Predictions and confusion matrix 

```{r qda predictions}

qda.pred <- predict(qda.fit, newdata = TestData)
qda.class <- qda.pred$class

par(mfrow=c(1,1))
plot(qda.pred$posterior[,2], qda.pred$class, col=TestData$RESPONSE+10)

```

```{r confusion matrix qda}

confusionMatrix(as.factor(qda.class), as.factor(TestData$RESPONSE))
cm <- confusionMatrix(as.factor(qda.class), as.factor(TestData$RESPONSE))

draw_confusion_matrix(cm)

``` 
 
#### MDA 

##### Definition

> For Mixture Discriminant Analysis, there are classes, and each class is assumed to be a Gaussian mixture of subclasses, where each data point has a probability of belonging to each class. Equality of covariance matrix, among classes, is still assumed.

(source: http://www.sthda.com/english/articles/36-classification-methods-essentials/146-discriminant-analysis-essentials-in-r/)

##### Fitting the model 

```{r fit mda}

#library(mda)
mda.fit <- mda(RESPONSE ~., data = TrainData, subset = TrainData$OBS)
mda.fit

```

##### Predictions and confusion matrix 

```{r mda predictions}

mda.pred <- predict(mda.fit, newdata = TestData)

mda.class <- mda.pred$class #show error for me :( 

```

```{r confusion matrix mda}

confusionMatrix(as.factor(mda.class), as.factor(TestData$RESPONSE))
cm <- confusionMatrix(as.factor(mda.class), as.factor(TestData$RESPONSE))

draw_confusion_matrix(cm)
```  


#### FDA 

##### Definition

> Flexible Discriminant Analysis is a flexible extension of LDA that uses non-linear combinations of predictors such as splines. FDA is useful to model multivariate non-normality or non-linear relationships among variables within each group, allowing for a more accurate classification.

(source: http://www.sthda.com/english/articles/36-classification-methods-essentials/146-discriminant-analysis-essentials-in-r/)

##### Fitting the model 

```{r fit qda}

fda.fit <- fda(RESPONSE ~., data = TrainData, subset = TrainData$OBS)
fda.fit

```

##### Predictions and confusion matrix 

```{r lda predictions}

fda.pred <- predict(fda.fit, newdata = TestData)
fda.class <- fda.pred$class

```

```{r confusion matrix lda}

confusionMatrix(as.factor(fda.class), as.factor(TestData$RESPONSE))
cm <- confusionMatrix(as.factor(fda.class), as.factor(TestData$RESPONSE))

draw_confusion_matrix(cm)
```  


### Random Forest

#### Model name

##### Definition

> Random forests or random decision forests are an ensemble learning method for classification, regression and other tasks that operate by constructing a multitude of decision trees at training time and outputting the class that is the mode of the classes (classification) or mean/average prediction (regression) of the individual trees. 

(source: https://en.wikipedia.org/wiki/Random_forest)

##### Fitting the model 

```{r random forest fit}

#library(randomForest)
#library(funModeling)

rf.fit <- randomForest(RESPONSE ~., 
                       TrainData, 
                       ntree = 500, 
                       mtry = 4, 
                       importance = TRUE, 
                       replace = FALSE)

```

##### Predictions and confusion matrix 

```{r results rf, fig.asp=1.5}

print(rf.fit)

#Variable importance analysis

importance(rf.fit) 
varImpPlot(rf.fit, main ='xxxx')

#two criteria: MeanDecreaseAccuracy (rough estimate of the loss in prediction performance when that particular variable is omitted from the training set) and Mean Decrease Gini (GINI is a measure of node impurity, highest purity means that each node contains only elements of a single class. Assessing the decrease in GINI when that feature is omitted leads to an understanding of how important that feature is to split the data correctly)

```


```{r rf prediction}

#obtain probability
rf.pred <- predict(rf.fit, newdata = TestData, type = "class")

#output of the prediction
rf.pred <- ifelse(rf.pred < 0.5, 0, 1)

```


```{r rf confusion matrix}

confusionMatrix(as.factor(rf.pred), as.factor(TestData$RESPONSE))
cm <- confusionMatrix(as.factor(rf.pred), as.factor(TestData$RESPONSE))
draw_confusion_matrix(cm)

```


### XGBoost 

#### Model name

##### Definition

##### Fitting the model 

```{r fit xgboost}

#library(xgboost)
#library(data.table)
#library(mlr)


train <- TrainData %>%
  mutate(dataset = "train")

train$RESPONSE<- as.factor(train$RESPONSE)


test <- TestData %>%
  mutate(dataset = "test")

test$RESPONSE<- as.factor(test$RESPONSE)


combined <- bind_rows(train, test)

# Impute missing values by field type
imp <- impute(
  combined,
  classes = list(
    factor = imputeMode(),
    integer = imputeMean(),
    numeric = imputeMean()
  )
)
combined <- imp$data

# Show column summary
summarizeColumns(combined) %>%
  kable(digits = 2)

#model works better when the explanatory features are on the same scale

combined <- normalizeFeatures(combined, target = "RESPONSE")
summarizeColumns(combined) %>%
  kable(digits = 2)

######### Convert factors to dummy variables ####################################

combined <- createDummyFeatures(
  combined, target = "RESPONSE",
  cols = c(
    "PURPOSE",
    "PROPERTY",
    "RESIDENCE"
  )
)

summarizeColumns(combined) %>%
  kable(digits = 2)

####We split it again

train <- combined %>%
  filter(dataset == "train") %>%
  select(-dataset)

test <- combined %>%
  filter(dataset == "test") %>%
  select(-dataset)


trainTask <- makeClassifTask(data = train, target = "RESPONSE", positive = 1)
testTask <- makeClassifTask(data = test, target = "RESPONSE")

#again stablish set seed

set.seed(1)

# Create an xgboost learner that is classification based and outputs
# labels (as opposed to probabilities)

xgb_learner <- makeLearner(
  "classif.xgboost",
  predict.type = "response",
  par.vals = list(
    objective = "binary:logistic",
    eval_metric = "error",
    nrounds = 100L,
    eta=0.1
  )
)


#set parameter space
params <- makeParamSet( makeDiscreteParam("booster",values = c("gbtree","gblinear")),
                        makeIntegerParam("max_depth",lower = 3L,upper = 10L),
                        makeNumericParam("min_child_weight",lower = 1L,upper = 10L),
                        makeNumericParam("subsample",lower = 0.5,upper = 1),
                        makeNumericParam("colsample_bytree",lower = 0.5,upper = 1))

#set resampling strategy
rdesc <- makeResampleDesc("CV",stratify = T,iters=5L)


#search strategy
ctrl <- makeTuneControlRandom(maxit = 10L)


```


##### Hyper-parameter Tuning

```{r xgboost tuning}

mytune <- tuneParams(learner = xgb_learner, 
                     task = trainTask, resampling = rdesc, 
                     measures = acc, par.set = params, control = ctrl, show.info = T)

mytune$y #0.7639


#set hyperparameters
xgb_learner_tune <- setHyperPars(xgb_learner,par.vals = mytune$x)

#train model
xgmodel <- train(learner = xgb_learner_tune,task = trainTask,)




```


##### Predictions 

```{r xgboost predictions}

xgpred <- predict(xgmodel,testTask)

```


```{r confusion matrix xgboost}

confusionMatrix(xgpred$data$response,xgpred$data$truth)
#Accuracy : 0.7711 <- better accuracy than our default xgboost model

```  



