# Model 

```{r confusion matrix draw function, include=FALSE}

############# Function for draw the confussion matrix####################################

draw_confusion_matrix <- function(cm) {

  layout(matrix(c(1,1,2)))
  par(mar=c(2,2,2,2))
  plot(c(100, 345), c(300, 450), type = "n", xlab="", ylab="", xaxt='n', yaxt='n')
  title('CONFUSION MATRIX', cex.main=2)

  # create the matrix 
  rect(150, 430, 240, 370, col='#3F97D0')
  text(195, 435, '0', cex=1.2)
  rect(250, 430, 340, 370, col='#F7AD50')
  text(295, 435, '1', cex=1.2)
  text(125, 370, 'Predicted', cex=1.3, srt=90, font=2)
  text(245, 450, 'Actual', cex=1.3, font=2)
  rect(150, 305, 240, 365, col='#F7AD50')
  rect(250, 305, 340, 365, col='#3F97D0')
  text(140, 400, '0', cex=1.2, srt=90)
  text(140, 335, '1', cex=1.2, srt=90)

  # add in the cm results 
  res <- as.numeric(cm$table)
  text(195, 400, res[1], cex=1.6, font=2, col='white')
  text(195, 335, res[2], cex=1.6, font=2, col='white')
  text(295, 400, res[3], cex=1.6, font=2, col='white')
  text(295, 335, res[4], cex=1.6, font=2, col='white')

  # add in the specifics 
  plot(c(100, 0), c(100, 0), type = "n", xlab="", ylab="", 
       main = "DETAILS", xaxt='n', yaxt='n')
  text(10, 85, names(cm$byClass[1]), cex=1.2, font=2)
  text(10, 70, round(as.numeric(cm$byClass[1]), 3), cex=1.2)
  text(30, 85, names(cm$byClass[2]), cex=1.2, font=2)
  text(30, 70, round(as.numeric(cm$byClass[2]), 3), cex=1.2)
  text(50, 85, names(cm$byClass[5]), cex=1.2, font=2)
  text(50, 70, round(as.numeric(cm$byClass[5]), 3), cex=1.2)
  text(70, 85, names(cm$byClass[6]), cex=1.2, font=2)
  text(70, 70, round(as.numeric(cm$byClass[6]), 3), cex=1.2)
  text(90, 85, names(cm$byClass[7]), cex=1.2, font=2)
  text(90, 70, round(as.numeric(cm$byClass[7]), 3), cex=1.2)

  # add in the accuracy information 
  text(30, 35, names(cm$overall[1]), cex=1.5, font=2)
  text(30, 20, round(as.numeric(cm$overall[1]), 3), cex=1.4)
  text(70, 35, names(cm$overall[2]), cex=1.5, font=2)
  text(70, 20, round(as.numeric(cm$overall[2]), 3), cex=1.4)
}  

```


## Select modeling technique

The modelling technique that we will be using are the following:

------> it is still not finish <------------ 


| n° | Model        |  Definition | 
|:--:|:-------------|:--------------|   
| 1  | Logistic <br /> regression   | > Logistic regression is a statistical model that in its basic form uses a logistic function to model a binary dependent variable, although many more complex extensions exist. In regression analysis, logistic regression (or logit regression) is estimating the parameters of a logistic model (a form of binary regression). 
(https://en.wikipedia.org/wiki/Logistic_regression) |
| 2  | Decision <br /> trees        |   |
| 3  | Discriminate <br /> analysis |   |
| 4  | Random <br /> forest         |   |
| 5  | Neural <br /> network        |   |
| 6  | XGBoost                      |   |


In order to compare the 6 models show before applying the CAREt library.

## Generate test design 

$$H_ {0}$$: The $Model_n$ give the best accuracy and sensitivity.

$$H_ {1}$$: It do not give the best values. 

Where $n= (1,2,3,4,5,6)$ and represent each model choosen in the selection technique section.


## Build model

Firstly, we need to standardize the data, as the variables have different scales. We will normalize only the continuous variables, as the categorical and dummy variables have only few different levels.  

```{r scaling, warning=FALSE, message=FALSE, echo=FALSE}

#selecting only the continuous variables to scale them

p1<- data_sel %>%  
      tidyr::gather(variable, value, c("DURATION", "AMOUNT", "INSTALL_RATE", 
                                       "AGE", "NUM_CREDITS")) %>% 
      ggplot(aes(x = variable, y = value, fill = variable)) + 
      geom_boxplot() +
      theme_bw() +
      coord_flip()+
      theme(legend.position="none")+
      theme(legend.title = element_blank())
      
      
data_scale <- data_sel %>% 
                dplyr::select(DURATION, AMOUNT, INSTALL_RATE, AGE, NUM_CREDITS) %>% 
                scale() %>%  #normalization
                as.data.frame()

#recreating the other variables to add them back to the dataset of the scaled ones 

data_scale %<>% mutate(
  CHK_ACCT = data_sel$CHK_ACCT,
  HISTORY = data_sel$HISTORY,
  PURPOSE = data_sel$PURPOSE,
  SAV_ACCT = data_sel$SAV_ACCT,
  EMPLOYMENT = data_sel$EMPLOYMENT,
  SEX_MALE = data_sel$SEX_MALE,
  MALE_SINGLE = data_sel$MALE_SINGLE,
  MALE_MAR_WID = data_sel$MALE_MAR_WID,
  CO_APPLICANT = data_sel$CO_APPLICANT,
  GUARANTOR = data_sel$GUARANTOR,
  PRESENT_RESIDENT = data_sel$PRESENT_RESIDENT,
  PROPERTY = data_sel$PROPERTY,
  OTHER_INSTALL = data_sel$OTHER_INSTALL,
  RESIDENCE = data_sel$RESIDENCE,
  JOB = data_sel$JOB, 
  RESPONSE = data_sel$RESPONSE
)

#reordering variable in the dataset

data_scale %<>% 
  dplyr::select(CHK_ACCT,DURATION,HISTORY,PURPOSE,AMOUNT,SAV_ACCT,EMPLOYMENT,
         INSTALL_RATE,SEX_MALE,MALE_SINGLE,MALE_MAR_WID,CO_APPLICANT,GUARANTOR,
         PRESENT_RESIDENT,PROPERTY,AGE,OTHER_INSTALL,RESIDENCE,NUM_CREDITS,JOB,RESPONSE)


p2<- data_scale %>%  
      tidyr::gather(variable, value, c("DURATION", "AMOUNT", "INSTALL_RATE", 
                                       "AGE", "NUM_CREDITS")) %>% 
      ggplot(aes(x = variable, y = value, fill = variable)) + 
      geom_boxplot() + 
      theme_bw() +
      coord_flip()+ 
      theme(legend.position="bottom")+
      theme(legend.title = element_blank())

gridExtra::grid.arrange(p1, p2, ncol=2, nrow = 1)

rm(p1, p2)

##################quetion--> it is ok that we have negatives values##################

```

Now that the normalization is done, lets move on by creating a training and test set based on the data.This will be done by dividing it in a randomly selection into the two subsets, with 75% of the data in the training set and the remaining 25% in the test set.


```{r test and training sets, warning=FALSE, message=FALSE, echo=FALSE}

#so that we always have the same division
set.seed(2311)


#creation of the index to divide the data in the two subsets
val_index<-createDataPartition(data_scale$RESPONSE, 
                               p=0.75, list=FALSE)

#########training dataset
TrainData<-as.data.frame(data_scale[val_index,])

########test dataset
TestData <- data_scale[-val_index,]

####################graph############################################

#table for the graph of training and testing

names<- c("Total", "Train", "Test")
values<- c(999, 750, 249)

p0<- gridExtra::grid.arrange(tableGrob(data.frame(names,values))) 

p1<- ggplot2::ggplot(data=data_scale, aes(x= RESPONSE, fill=RESPONSE)) +
        geom_bar(aes(y = (..count..)/sum(..count..)))+
        scale_y_continuous(labels=scales::percent) +
        ylab("Freq")

p2<- ggplot2::ggplot(data=TrainData, aes(x= RESPONSE, fill=RESPONSE)) +
        geom_bar(aes(y = (..count..)/sum(..count..)))+
        scale_y_continuous(labels=scales::percent) +
        ylab("Freq")

p3<- ggplot2::ggplot(data=TestData, aes(x= RESPONSE, fill=RESPONSE)) +
        geom_bar(aes(y = (..count..)/sum(..count..)))+
        scale_y_continuous(labels=scales::percent) +
        ylab("Freq")


grid.arrange(p0, p1, p2, p3, ncol=2)

rm(p1, p0, p2, p3, names, values) #delete variables

######### missing the tittles##################################################

```

As, you can see below the data have the same proportion in the dataset, the training and the testing set. We can now move to the modelization. 

### M1: Logistic regression

\[ Z_{i} = ln(\frac{P_{i}} {1-P_{i}}) = \beta_0+\beta_1X_1+...+\beta_nX_n \]

To do so, we are going follow 6 steps:

1) Fitting the model with no balance data
2) Prediction
3) Evaluation of the prediction
4) Fitting the model with balance data
5) Prediction
6) Evaluation of the prediction

#### {.tabset .tabset-fade .tabset-pills}


##### Fitting the model

```{r glm-model, echo=FALSE, warning=FALSE, message=FALSE}

#Same division
set.seed(1234)

#########################model######################################vvvv
train_params <- trainControl(method = "repeatedcv", number = 10, repeats=5) #K-Fold Cross Validation
mod_lg_fit <- caret::train(RESPONSE ~ ., TrainData, method="glm", 
                           family="binomial",trControl= train_params)

################check outputs################################vv
summary(mod_lg_fit)


```

##### Coefficients 

```{r echo=FALSE, message=FALSE, warning=FALSE}

#########NOT SURE IF THIS IS NECESSARY#######################
##variable is significance--> high coefficient = bring high information

temp <- summary(mod_lg_fit)$coeff[-1,4] < 0.05

############condition: yes or not#####################################

temp %<>% as.data.frame()  

kable(temp, caption = "Significance of variable")

#remove variable temp
rm(temp) 

#########################################################################

mod_lg_fit$coefnames

#########################################################################

```

##### Prediction (unbalance)

```{r predictions lg, echo=FALSE, message=FALSE, warning=FALSE}

#prediction given the model
lg.pred <- predict(mod_lg_fit, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (Unbalance)

```{r confusion matrix lg, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(lg.pred), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)
#############remove temporary element
rm(cm)

#### save the variables#######

sens<- caret::sensitivity(table(as.factor(lg.pred), as.factor(TestData$RESPONSE)))
sp<- caret::specificity(table(as.factor(lg.pred), as.factor(TestData$RESPONSE)))
acc<- 0.791

logistic<- c(sens , sp, acc)

#############remove temporary element
rm(cm, sens, sp, acc)

```

##### Fitting the model: balance

```{r glm-model, echo=FALSE, warning=FALSE, message=FALSE}

#Same division
set.seed(1234)

#########################model######################################
train_params <- caret::trainControl(method = "repeatedcv", number = 10, 
                                    repeats=5, sampling = "down", 
                                    summaryFunction = twoClassSummary)

mod_lg_fitbalance <- caret::train(RESPONSE ~ ., TrainData, method="glm", 
                                  family="binomial", 
                                  metric = "Sens", #optimize sensitivity
                                  maximize = TRUE, #maximize the metric
                                  trControl= train_params)

################check outputs################################vv
summary(mod_lg_fitbalance)


```

##### Prediction

```{r predictions lgb, echo=FALSE, message=FALSE, warning=FALSE}
#probability given the model

lg.pred.b <- predict(mod_lg_fitbalance, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (balance)

```{r confusion matrix lgb, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(lg.pred.b), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

#### save the variables#######

sens.b<- caret::sensitivity(table(as.factor(lg.pred.b), as.factor(TestData$RESPONSE)))
sp.b<- caret::specificity(table(as.factor(lg.pred.b), as.factor(TestData$RESPONSE)))
acc.b<- 0.671

logistic_balance<- c(sens.b , sp.b, acc.b)

#############remove temporary element
rm(cm, sens.b, sp.b, acc.b)

```

####


### M2: Decision trees

#### {.tabset .tabset-fade .tabset-pills}


##### Fitting the model

```{r rpart ,echo=FALSE, message=FALSE, warning=FALSE}

#Same division
set.seed(1234)

#########################model######################################
train_params <- trainControl(method = "repeatedcv", number = 10, repeats=5) #K-Fold Cross Validation
mod_dt_fit <- caret::train(RESPONSE ~ ., TrainData, method="rpart", 
                           trControl= train_params)

################check outputs################################vv
summary(mod_dt_fit$finalModel)


```

##### Plot (Unbalance)

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.asp=1.5}

#######plot option 1 #########################
##plot(mod_dt_fit$finalModel, uniform=TRUE,
##     main="Classification Tree")
##text(mod_dt_fit$finalModel, use.n.=TRUE, all=TRUE, cex=.8)


#######plot option 2 #########################
suppressMessages(library(rattle))
rattle::fancyRpartPlot(mod_dt_fit$finalModel)


```

##### Prediction (unbalance)

```{r predictions rpart, echo=FALSE, message=FALSE, warning=FALSE}

#prediction given the model
dt.pred <- predict(mod_dt_fit, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (Unbalance)

```{r confusion matrix rpart, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(dt.pred), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

#############Parameters

sens<- caret::sensitivity(table(as.factor(dt.pred), as.factor(TestData$RESPONSE)))
sp<- caret::specificity(table(as.factor(dt.pred), as.factor(TestData$RESPONSE)))
acc<- 0.739

decision_tree<- c(sens , sp, acc)

#############remove temporary element
rm(cm, sens, sp, acc)


```

##### Fitting the model: balance

```{r rpart-model, echo=FALSE, warning=FALSE, message=FALSE}

#Same division
set.seed(1234)

#########################model######################################

train_params <- caret::trainControl(method = "repeatedcv", number = 10, 
                                    repeats=5, sampling = "down", 
                                    summaryFunction = twoClassSummary)

mod_dt_fitbalance <- caret::train(RESPONSE ~ ., TrainData, method="rpart", 
                                  metric = "Sens", #optimize sensitivity
                                  maximize = TRUE, #maximize the metric
                                  trControl= train_params)

################check outputs################################
summary(mod_dt_fitbalance$finalModel)


```

##### Plot (balance)

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.asp=1.5}

#######plot option 1 #########################
##plot(mod_dt_fitbalance$finalModel, uniform=TRUE,
##     main="Classification Tree")
##text(mod_dt_fitbalance$finalModel, use.n.=TRUE, all=TRUE, cex=.8)


#######plot option 2 #########################
suppressMessages(library(rattle))
rattle::fancyRpartPlot(mod_dt_fitbalance$finalModel)


```

##### Prediction

```{r predictions rpartb, echo=FALSE, message=FALSE, warning=FALSE}
#probability given the model

dt.pred.b <- predict(mod_dt_fitbalance, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (balance)

```{r confusion matrix rpartb, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(dt.pred.b), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)
#############Parameters

sens.b<- caret::sensitivity(table(as.factor(dt.pred.b), as.factor(TestData$RESPONSE)))
sp.b<- caret::specificity(table(as.factor(dt.pred.b), as.factor(TestData$RESPONSE)))
acc.b<- 0.606

decision_tree_balance<- c(sens.b , sp.b, acc.b)

#############remove temporary element
rm(cm, sens.b, sp.b, acc.b)


```


####


### M3: Discriminate analysis

#### LDA {.tabset .tabset-fade .tabset-pills}

##### Fitting the model

```{r lda-model ,echo=FALSE, message=FALSE, warning=FALSE}

#Same division
set.seed(1234)

#########################model######################################vvvv
train_params <- trainControl(method = "repeatedcv", number = 10, repeats=5) #K-Fold Cross Validation
mod_lda_fit <- caret::train(RESPONSE ~ ., TrainData, method="lda", 
                           family="binomial",trControl= train_params)

################check outputs################################vv
summary(mod_lda_fit)


```


##### Prediction (unbalance)

```{r predictions lda, echo=FALSE, message=FALSE, warning=FALSE}

lda.pred <- predict(mod_lda_fit, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (Unbalance)

```{r confusion matrix lda, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(lda.pred), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)
#############
sens<- caret::sensitivity(table(as.factor(lda.pred), as.factor(TestData$RESPONSE)))
sp<- caret::specificity(table(as.factor(lda.pred), as.factor(TestData$RESPONSE)))
acc<- 0.783

lda<- c(sens , sp, acc)

#############remove temporary element
rm(cm, sens, sp, acc)


```

##### Fitting the model: balance

```{r ldab-model, echo=FALSE, warning=FALSE, message=FALSE}

#########################model######################################
train_params <- caret::trainControl(method = "repeatedcv", number = 10, 
                                    repeats=5, sampling = "down", 
                                    summaryFunction = twoClassSummary)


mod_lda_fitbalance <- caret::train(RESPONSE ~ ., TrainData, method="lda", 
                           family="binomial",
                           metric = "Sens", #optimize sensitivity
                           maximize = TRUE, #maximize the metric
                           trControl= train_params)

################check outputs################################vv
summary(mod_lda_fitbalance)


```


##### Prediction

```{r predictions ldab, echo=FALSE, message=FALSE, warning=FALSE}

lda.pred.b <- predict(mod_lda_fitbalance, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (balance)

```{r confusion matrix ldab, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(lda.pred.b), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

#########

sens.b<- caret::sensitivity(table(as.factor(lda.pred.b), as.factor(TestData$RESPONSE)))
sp.b<- caret::specificity(table(as.factor(lda.pred.b), as.factor(TestData$RESPONSE)))
acc.b<- 0.695

lda_balance<- c(sens.b , sp.b, acc.b)

#############remove temporary element
rm(cm, sens.b, sp.b, acc.b)


```

####




#### QDA {.tabset .tabset-fade .tabset-pills}

##### Fitting the model

```{r qda-model ,echo=FALSE, message=FALSE, warning=FALSE}

#Same division
set.seed(1234)

#########################model######################################vvvv
train_params <- trainControl(method = "repeatedcv", number = 10, repeats=5) #K-Fold Cross Validation
mod_qda_fit <- caret::train(RESPONSE ~ ., TrainData, method="qda", 
                           family="binomial",trControl= train_params)

################check outputs################################vv
summary(mod_qda_fit)


```


##### Prediction (unbalance)

```{r predictions qda, echo=FALSE, message=FALSE, warning=FALSE}

qda.pred <- predict(mod_qda_fit, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (Unbalance)

```{r confusion matrix qda, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(qda.pred), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

#############
sens<- caret::sensitivity(table(as.factor(qda.pred), as.factor(TestData$RESPONSE)))
sp<- caret::specificity(table(as.factor(qda.pred), as.factor(TestData$RESPONSE)))
acc<- 0.763

qda<- c(sens , sp, acc)

#############remove temporary element
rm(cm, sens, sp, acc)



```

##### Fitting the model: balance

```{r qdab-model, echo=FALSE, warning=FALSE, message=FALSE}

#########################model######################################
train_params <- caret::trainControl(method = "repeatedcv", number = 10, 
                                    repeats=5, sampling = "down", 
                                    summaryFunction = twoClassSummary)


mod_qda_fitbalance <- caret::train(RESPONSE ~ ., TrainData, method="qda", 
                           family="binomial",
                           metric = "Sens", #optimize sensitivity
                           maximize = TRUE, #maximize the metric
                           trControl= train_params)

################check outputs################################vv
summary(mod_qda_fitbalance)


```


##### Prediction

```{r predictions qdab, echo=FALSE, message=FALSE, warning=FALSE}

qda.pred.b <- predict(mod_qda_fitbalance, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (balance)

```{r confusion matrix qdab, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(qda.pred.b), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)
#########

sens.b<- caret::sensitivity(table(as.factor(qda.pred.b), as.factor(TestData$RESPONSE)))
sp.b<- caret::specificity(table(as.factor(qda.pred.b), as.factor(TestData$RESPONSE)))
acc.b<- 0.679

qda_balance<- c(sens.b , sp.b, acc.b)

#############remove temporary element
rm(cm, sens.b, sp.b, acc.b)



```

####




#### FDA {.tabset .tabset-fade .tabset-pills}

##### Fitting the model

```{r fda-model ,echo=FALSE, message=FALSE, warning=FALSE}

#Same division
set.seed(1234)

#########################model######################################vvvv
train_params <- trainControl(method = "repeatedcv", number = 10, repeats=5) #K-Fold Cross Validation

library(earth)
mod_fda_fit <- caret::train(RESPONSE ~ ., TrainData, method="fda", 
                              trControl= train_params)

################check outputs################################vv
summary(mod_fda_fit)


```


##### Prediction (unbalance)

```{r predictions fda, echo=FALSE, message=FALSE, warning=FALSE}

fda.pred <- predict(mod_fda_fit, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (Unbalance)

```{r confusion matrix fda, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(fda.pred), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

#############
sens<- caret::sensitivity(table(as.factor(fda.pred), as.factor(TestData$RESPONSE)))
sp<- caret::specificity(table(as.factor(fda.pred), as.factor(TestData$RESPONSE)))
acc<- 0.759

fda<- c(sens , sp, acc)

#############remove temporary element
rm(cm, sens, sp, acc)


```

##### Fitting the model: balance

```{r fdab-model, echo=FALSE, warning=FALSE, message=FALSE}

#########################model######################################
train_params <- caret::trainControl(method = "repeatedcv", number = 10, 
                                    repeats=5, sampling = "down", 
                                    summaryFunction = twoClassSummary)

mod_fda_fitbalance <- caret::train(RESPONSE ~ ., TrainData, method="fda", 
                                   metric = "Sens", #optimize sensitivity
                                    maximize = TRUE,
                                    trControl= train_params)

################check outputs################################vv
summary(mod_fda_fitbalance)


```


##### Prediction

```{r predictions fdab, echo=FALSE, message=FALSE, warning=FALSE}

fda.pred.b <- predict(mod_fda_fitbalance, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (balance)

```{r confusion matrix fdab, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(fda.pred.b), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

#####################

sens.b<- caret::sensitivity(table(as.factor(fda.pred.b), as.factor(TestData$RESPONSE)))
sp.b<- caret::specificity(table(as.factor(fda.pred.b), as.factor(TestData$RESPONSE)))
acc.b<- 0.598

fda_balance<- c(sens.b , sp.b, acc.b)

#############remove temporary element
rm(cm, sens.b, sp.b, acc.b)



```

####





#### MDA {.tabset .tabset-fade .tabset-pills}

##### Fitting the model

```{r mda-model ,echo=FALSE, message=FALSE, warning=FALSE}

#Same division
set.seed(1234)

#########################model######################################vvvv
train_params <- trainControl(method = "repeatedcv", number = 10, repeats=5) #K-Fold Cross Validation
mod_mda_fit <- caret::train(RESPONSE ~ ., TrainData, method="mda", 
                           family="binomial",trControl= train_params)

################check outputs################################vv
summary(mod_mda_fit)


```


##### Prediction (unbalance)

```{r predictions mda, echo=FALSE, message=FALSE, warning=FALSE}

mda.pred <- predict(mod_mda_fit, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (Unbalance)

```{r confusion matrix mda, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(mda.pred), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)
#############remove temporary element
sens<- caret::sensitivity(table(as.factor(mda.pred), as.factor(TestData$RESPONSE)))
sp<- caret::specificity(table(as.factor(mda.pred), as.factor(TestData$RESPONSE)))
acc<- 0.739

mda<- c(sens , sp, acc)

#############remove temporary element
rm(cm, sens, sp, acc)


```

##### Fitting the model: balance

```{r mdab-model, echo=FALSE, warning=FALSE, message=FALSE}

#########################model######################################
train_params <- caret::trainControl(method = "repeatedcv", number = 10, 
                                    repeats=5, sampling = "down", 
                                    summaryFunction = twoClassSummary)

mod_mda_fitbalance <- caret::train(RESPONSE ~ ., TrainData, method="mda", 
                           family="binomial",
                           metric = "Sens", #optimize sensitivity
                           maximize = TRUE,
                           trControl= train_params)

################check outputs################################vv
summary(mod_mda_fitbalance)


```


##### Prediction

```{r predictions mdab, echo=FALSE, message=FALSE, warning=FALSE}

mda.pred.b <- predict(mod_mda_fitbalance, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (balance)

```{r confusion matrix mdab, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(mda.pred.b), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

#########

sens.b<- caret::sensitivity(table(as.factor(mda.pred.b), as.factor(TestData$RESPONSE)))
sp.b<- caret::specificity(table(as.factor(mda.pred.b), as.factor(TestData$RESPONSE)))
acc.b<- 0.675

mda_balance<- c(sens.b , sp.b, acc.b)

#############remove temporary element
rm(cm, sens.b, sp.b, acc.b)


```

####



### M4: Random Forest

#### {.tabset .tabset-fade .tabset-pills}


##### Fitting the model

```{r rf-model, echo=FALSE, message=FALSE, warning=FALSE}

#Same division
set.seed(1234)

#########################model######################################vvvv
train_params <- trainControl(method = "repeatedcv", number = 10, repeats=5) #K-Fold Cross Validation
mod_rf_fit <- caret::train(RESPONSE ~ ., TrainData, method="rf", 
                           trControl= train_params)

################check outputs################################vv
summary(mod_rf_fit)


```

##### Prediction (unbalance)

```{r predictions rf, echo=FALSE, message=FALSE, warning=FALSE}

rf.pred <- predict(mod_rf_fit, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (Unbalance)

```{r confusion matrix rf, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(rf.pred), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)
############
sens<- caret::sensitivity(table(as.factor(rf.pred), as.factor(TestData$RESPONSE)))
sp<- caret::specificity(table(as.factor(rf.pred), as.factor(TestData$RESPONSE)))
acc<- 0.747

rf<- c(sens , sp, acc)

#############remove temporary element
rm(cm, sens, sp, acc)


```

##### Fitting the model: balance

```{r rfb-model, echo=FALSE, warning=FALSE, message=FALSE}

train_params <- caret::trainControl(method = "repeatedcv", number = 10, 
                                    repeats=5, sampling = "down", 
                                    summaryFunction = twoClassSummary)

mod_rf_fitbalance <- caret::train(RESPONSE ~ ., TrainData, method="rf", 
                           family="binomial",
                           metric = "Sens", #optimize sensitivity
                           maximize = TRUE,
                           trControl= train_params)

################check outputs################################vv
summary(mod_rf_fitbalance)


```


##### Prediction

```{r predictions rfb, echo=FALSE, message=FALSE, warning=FALSE}

rf.pred.b <- predict(mod_rf_fitbalance, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (balance)

```{r confusion matrix mdab, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(rf.pred.b), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)
######################

sens.b<- caret::sensitivity(table(as.factor(rf.pred.b), as.factor(TestData$RESPONSE)))
sp.b<- caret::specificity(table(as.factor(rf.pred.b), as.factor(TestData$RESPONSE)))
acc.b<- 0.651

rf_balance<- c(sens.b , sp.b, acc.b)

#############remove temporary element
rm(cm, sens.b, sp.b, acc.b)



```

####





### M5: Neural Networks

#### {.tabset .tabset-fade .tabset-pills}

##### Fitting the model

```{r nn-model, echo=FALSE, message=FALSE, warning=FALSE}

#Same division
set.seed(1234)

#########################model######################################vvvv
train_params <- trainControl(method = "repeatedcv", number = 10, repeats=5) #K-Fold Cross Validation
mod_nn_fit <- caret::train(RESPONSE ~ ., TrainData, method="nnet", 
                           trControl= train_params)

################check outputs################################

#summary(mod_nn_fit) #this is very long

```

##### plot

```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.asp=2}

library(nnet)
NeuralNetTools::plotnet(mod_nn_fit$finalModel, y_names = "yes/no")
title("Graphical Representation of our Neural Network")


```

##### Prediction (unbalance)

```{r predictions nn, echo=FALSE, message=FALSE, warning=FALSE}

nn.pred <- predict(mod_nn_fit, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (Unbalance)

```{r confusion matrix nn, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(nn.pred), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

#############

sens<- caret::sensitivity(table(as.factor(nn.pred), as.factor(TestData$RESPONSE)))
sp<- caret::specificity(table(as.factor(nn.pred), as.factor(TestData$RESPONSE)))
acc<- 0.763

nn<- c(sens , sp, acc)

#############remove temporary element
rm(cm, sens, sp, acc)


```

##### Fitting the model: balance

```{r nnb-model, echo=FALSE, warning=FALSE, message=FALSE}

train_params <- caret::trainControl(method = "repeatedcv", number = 10, 
                                    repeats=5, sampling = "down", 
                                    summaryFunction = twoClassSummary)

mod_nn_fitbalance <- caret::train(RESPONSE ~ ., TrainData, method="nnet", 
                           family="binomial",
                           metric = "Sens", #optimize sensitivity
                           maximize = TRUE,
                           trControl= train_params)

################check outputs################################
summary(mod_nn_fitbalance)


```


##### Prediction

```{r predictions nnb, echo=FALSE, message=FALSE, warning=FALSE}

nn.pred.b <- predict(mod_nn_fitbalance, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (balance)

```{r confusion matrix nnb, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(nn.pred.b), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

######################

sens.b<- caret::sensitivity(table(as.factor(nn.pred.b), as.factor(TestData$RESPONSE)))
sp.b<- caret::specificity(table(as.factor(nn.pred.b), as.factor(TestData$RESPONSE)))
acc.b<- 0.679

nn_balance<- c(sens.b , sp.b, acc.b)

#############remove temporary element
rm(cm, sens.b, sp.b, acc.b)



```

####



### M6: XGBoost

#### {.tabset .tabset-fade .tabset-pills}


##### Fitting the model

```{r xgb-model, echo=FALSE, message=FALSE, warning=FALSE}

######################### transform data ############
data_xgboost <- map_df(data_scale, function(columna) {
                  columna %>% 
                  as.factor() %>% 
                  as.numeric %>% 
                  { . - 1 } })

test_xgboost <- sample_frac(data_xgboost, size = 0.249)
train_xgboost <- setdiff(data_xgboost, test_xgboost)


#Convertir a DMatrix

train_xgb_matrix <-   train_xgboost %>% 
                            dplyr::select(- RESPONSE) %>% 
                            as.matrix() %>% 
                            xgboost::xgb.DMatrix(data = ., label = train_xgboost$RESPONSE)
#Convertir a DMatrix

test_xgb_matrix <-  test_xgboost %>% 
                            dplyr::select(- RESPONSE) %>% 
                            as.matrix() %>% 
                            xgboost::xgb.DMatrix(data = ., label = test_xgboost$RESPONSE)

#Same division
set.seed(1234)

#########################model######################################
train_params <- trainControl(method = "repeatedcv", 
                             number = 10, # with n folds 
                             repeats=5) #K-Fold Cross Validation

mod_xgb_fit <- caret::train(RESPONSE ~ ., TrainData, 
                           method="xgbTree", 
                           trControl= train_params)

################check outputs################################vv
summary(mod_xgb_fit)

```

##### plot

```{r , echo=FALSE, message=FALSE, warning=FALSE}

mod_xgb_fit$bestTune


```

##### Prediction (unbalance)

```{r predictions xgb, echo=FALSE, message=FALSE, warning=FALSE}

xgb.pred <- predict(mod_xgb_fit, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (Unbalance)

```{r confusion matrix xgb, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(xgb.pred), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

######################

sens<- caret::sensitivity(table(as.factor(xgb.pred), as.factor(TestData$RESPONSE)))
sp<- caret::specificity(table(as.factor(xgb.pred), as.factor(TestData$RESPONSE)))
acc<- 0.743

xgb<- c(sens , sp, acc)

#############remove temporary element
rm(cm, sens, sp, acc)


```

##### Fitting the model: balance

```{r xgbb-model, echo=FALSE, warning=FALSE, message=FALSE}

train_params <- caret::trainControl(method = "repeatedcv", number = 10, 
                                    repeats=5, sampling = "down", 
                                    summaryFunction = twoClassSummary)

mod_xgb_fitbalance <- caret::train(RESPONSE ~ ., TrainData, method="xgbTree", 
                            metric = "Sens", #optimize sensitivity
                           maximize = TRUE,
                           trControl= train_params)

################check outputs################################
summary(mod_xgb_fitbalance)


```


##### Prediction

```{r predictions xgbb, echo=FALSE, message=FALSE, warning=FALSE}

xgb.pred.b <- predict(mod_xgb_fitbalance, newdata = TestData)  #predict give me the probability i am looking for the the binomial answer

```

##### Diagnosis (balance)

```{r confusion matrix xgbb, echo=FALSE, message=FALSE, warning=FALSE}

#############confusion matrix 
cm <- confusionMatrix(as.factor(xgb.pred.b), as.factor(TestData$RESPONSE))
############draw of confusion matrix
draw_confusion_matrix(cm)

######################

sens.b<- caret::sensitivity(table(as.factor(xgb.pred.b), as.factor(TestData$RESPONSE)))
sp.b<- caret::specificity(table(as.factor(xgb.pred.b), as.factor(TestData$RESPONSE)))
acc.b<- 0.723

xgb_balance<- c(sens.b , sp.b, acc.b)

#############remove temporary element
rm(cm, sens.b, sp.b, acc.b)


```

####





## Assess model

```{r , echo=FALSE, message=FALSE, warning=FALSE}

Details<- c("Sensitivity", "Specificity", "Accuracy")
summary_table<- data.frame(Details, logistic, logistic_balance, 
                           decision_tree, decision_tree_balance,
                           lda, lda_balance, 
                           qda, qda_balance,
                           fda, fda_balance, 
                           mda, mda_balance,
                           rf, rf_balance,
                           nn, nn_balance,
                           xgb, xgb_balance)
                           

summary_table<-data.frame(t(summary_table[-1]))                           
names(summary_table) <- c("Sensitivity", "Specificity", "Accuracy")                          
                           
summary_table

```


